Appendix to 'Detecting social information in a dense database of infants’ natural

### 2022-01-05 paper/preprint/manuscript_dec2021_apa_blinded.Rmd
add discussion, intro paragraphs

Here, we examine the social information present in the infant visual perspective---the presence of faces and hands---by analyzing a longitudinal collection of more than 1700 headcam videos collected from three children along a span of 6 to 32 months of age—--the SAYCam dataset [@SAYcam]. In addition to its size and longitudinal nature, this dataset is more naturalistic than those previously used in two key ways. First, recordings were taken under a large variety of activity contexts [@roy2015predicting; @bruner1985role] encompassing infants' viewpoints during both activities outside and inside the home. Even in other naturalistic datasets, the incredible variety in a typical infant's experience has been largely underrepresented (see examples in Figure 1; e.g., riding in the car, gardening, watching chickens during a walk, browsing magazines, nursing, brushing teeth). Second, the head-mounted cameras used in the SAYCam dataset captured a larger field of view than those typically used, allowing a more complete picture of the infant perspective. While head-mounted cameras with a more restricted field of view do represent where infants are foveating most of the time [@yoshida2008; @smith2015contributions], they may fail when faces or hands appear in children's peripheral vision but are still part of a joint interaction.

With hundreds of hours of footage (>42M frames), however, this large dataset necessitates a shift to an automated annotation strategy.
Indeed, annotation of the frames extracted from egocentric videos has been prohibitively time-consuming, meaning that most frames are typically not inspected, even in the most comprehensive studies. 
For example, @Fausey2016 collected a total of 143 hours of head-mounted camera footage (15.5 million frames), of which one frame every five seconds was hand-annotated (by four coders), totalling 103,383 frames (per coder)—an impressive number of annotations but nonetheless only 0.67% of the collected footage.
To address this challenge, we use a modern computer vision model of pose detection to automatically detect the presence of hands and faces from the infant egocentric viewpoint. 
Specifically, we use OpenPose [@Cao2018openpose], a model optimized for jointly detecting human face, body, hand, and foot keypoints that operates well on scenes including multiple people, even if they are partially-occluded (see Figure 1). 
In prior work examining egocentric videos taken from the infant perspective, OpenPose performed comparably to other modern face detection models [@long2021automated].

In this paper, we first describe the dataset and validate the use of this model by comparing face and hand detections to a human-annotated set of 24,000 frames. 
Next, we report how the proportion of faces and hands changes with age in each of the three children in the dataset. 
We then investigate sources of variability in our more naturalistic dataset that may explain differences from prior work, including both the field-of-view of the head cameras as well as a diversity of locations in which videos were recorded.
Finally, making use of automated annotation of pose bounding boxes, we analyze the size, location, and variability of detected faces and poses across development.

@@

@@

# Variation with motor development
```{r}
motor = read_csv(file=here::here('data/raw_data/saycam_walking_asq.csv'))

# General Discussion
Here, we analyzed the social information in view in a dense, longitudinal dataset, applying a modern computer-vision model to quantify the hands and faces seen from each of three children's egocentric perspective from 6 to 32 months of age. First, we found a moderate decrease across age in the proportion of faces in view in the videos, in keeping with previous work [@Fausey2016; @Jayaraman2015]. 
This finding is particularly notable given that, in previous cross-sectional data, this effect seems to be most strongly driven by infants younger than 4 months of age [e.g., @Fausey2016; @Jayaraman2015; @Sugden2014] who see both more frequent and more persistent faces [@Jayaraman2018]. 
We also found this to be true when restricting our analyses to full-field faces, suggesting this effect is not driven by a concurrent shift from more full-view to partial-views of faces.

We also found an unexpectedly high proportion of hands in infants' view, even when restricting the field-of-view to the center field-of-view to make the viewpoints comparable to those of headcams used in prior work. 
Why might this be the case? One idea is that these videos contain the viewpoints of children not only during structured interactions (e.g., play sessions at home or in the lab) but during everyday activities when children may be playing by themselves or simply observing the actions of caregivers and other people in their environment. 
During these less structured times, caregivers may move about in the vicinity of the child but not interact with them as directly -- leading to views where a person and their hands are visible from a distance, but this person's face may be turned away from the infant or occluded (see examples in Figure 1). Indeed, using the same pose detector on videos from in-lab play sessions, @long2021automated found the opposite trend: slightly fewer hand detections than face detections from 8-16 months of age. Work that directly examines the variability in the social information in view across more vs. less structured activity contexts could further test this idea.

A coarse analysis based on the location the videos were filmed in further highlights the variability of the social information in view during different activities, showing differences across locations and between individual children. Within a given, well-defined context -- e.g., mealtime in kitchens -- S saw more faces than A, and S saw more faces in the kitchen than in other locations. This variability likely stems from the fact that there are at least three ways to feed a young child: 1) sitting in front of the child, facing them as they sit in a high chair; 2) sitting behind the child, holding them as they face outward, and 3) sitting side by side. Each of these positions offer the child differing degrees of visual access to faces and hands. While the social information in view may be variable across children in different activity contexts, these analyses suggest they could be stable within a given child's day-to-day experience.

@@

In future work, the adaptation of deep neural networks for the infant egocentric view remains a promising avenue for collaboration between computer vision experts and developmental psychologists. 
Indeed, this combination has already yielded new insights about the learning mechanisms needed to build visual representations [@tsutsui2020computational; @zhuang2020unsupervised; @orhan2020self]. 
We propose that the use of novel algorithms with large-scale analysis of dense datasets -- collected with different fields of view, cameras, and from many different laboratories -- will lead to generalizable conclusions about the regularities of infant experience that scaffold learning.

>>>>

Here, we examine the social information present in the infant visual perspective---the presence of faces and hands---by analyzing a longitudinal collection of more than 1700 headcam videos collected at home from three children along a span of 6 to 32 months of age—--the SAYCam dataset [@SAYcam]. We thus analyze the video data from this dense, longitudinal dataset as case studies of how the social information in the infant view changes over the course of development. These kinds of longitudinal case studies provide an important counterpoint to cross-sectional investigations for several reasons. By repeatedly recording data from the same child, they allow us to investigate developmental changes within each child and to relate these to developmental milestones (e.g., the onset of walking). Second, they eliminate several nuance sources of variability (e.g., parent/child familiarity with camera, home environment) that may obscure fine-grained developmental patterns.

Finally, longitudinal case studies allow us to investigate the ecological validity of results in everyday, naturalistic learning contexts. Indeed, in addition to its size and longitudinal nature, the SAYCam dataset is more naturalistic than those previously used in two key ways. First, recordings were taken under a large variety of activity contexts [@roy2015predicting; @bruner1985role] encompassing infants' viewpoints during both activities outside and inside the home. Even in other naturalistic datasets, the incredible variety in a typical infant's experience has been largely underrepresented (see examples in Figure 1; e.g., riding in the car, gardening, watching chickens during a walk, browsing magazines, nursing, brushing teeth). Second, the head-mounted cameras used in the SAYCam dataset captured a larger field of view than those typically used, allowing a more complete picture of the infant perspective. While head-mounted cameras with a more restricted field of view do represent where infants are foveating most of the time [@yoshida2008; @smith2015contributions], they may fail when faces or hands appear in children's peripheral vision but are still part of a joint interaction.

With hundreds of hours of footage (>42M frames), however, this large dataset necessitates a shift to an automated annotation strategy.
Indeed, annotation of the frames extracted from egocentric videos has been prohibitively time-consuming, meaning that most frames are typically not inspected, even in the most comprehensive studies. 
For example, @Fausey2016 collected a total of 143 hours of head-mounted camera footage (15.5 million frames), of which one frame every five seconds was hand-annotated (by four coders), totalling 103,383 frames (per coder)--an impressive number of annotations but nonetheless only 0.67% of the collected footage.

To address this challenge, we use a modern computer vision model of pose detection to automatically detect the presence of hands and faces from the infant egocentric viewpoint. 
Specifically, we use OpenPose [@Cao2018openpose], a model optimized for jointly detecting human face, body, hand, and foot keypoints. 
In prior work examining egocentric videos taken from the infant perspective during in-lab play sessions, OpenPose performed comparably to other modern face detection models [@long2021automated].
However, these at-home, naturalistic videos contain more cluttered visual environments, challenging lighting conditions, and many different novel viewpoints.
This this paper, we first validate the use of OpenPose by comparing face and hand detections to a human-annotated set of 24,000 frames. Overall, we find that OpenPose operates relatively on egocentric scenes including multiple people, even if they are partially-occluded (see Figure 1), nd and discuss the benefits and drawbacks of this automated annotation strategy.

We next capitalize on this computational advance to annotate the entirety of this large, longitudinal video dataset. We use these detections to report how the proportion of faces and hands changes with age and motor development milestones in each of the three children in the dataset. 
Weinvestigate sources of variability in our more naturalistic dataset that may explain differences from prior work, including both the field-of-view of the head cameras as well as a diversity of locations in which videos were recorded.
Finally, making use of automated annotation of pose bounding boxes, we analyze the size, location, and variability of detected faces and poses across development in these three children.

@@

## Variation with motor development
In a set of exploratory analyses, we examined how the onset of sitting, cruising, and walking in each individual child changed the proportion of faces and hands in view. Each parent completed the Ages and Stages Questionnaire (ASQ), and we coded the age at which each child reached each motor milestone. To do so, we used a mixed-effects regression with per-child random intercepts

We next examine whether the SAYcam participants' age of reaching particular developmental milestones (sitting, cruising, and walking) significantly influenced the amount of hands or faces that they saw, using a mixed-effects regression with per-child random intercepts.
[table with each child's age of onset per milestone?]

@@

# General Discussion
Here, we first validated the use of an automated pose detection model to detect the faces and hands in view in a longitudinal dataset of egocentric, everyday visual experience. We then used these detections to analyze the social information seen from each of three children's egocentric perspective from 6 to 32 months of age.

First, we found a moderate decrease across age in the proportion of faces in view in the videos, in keeping with previous work [@Fausey2016; @Jayaraman2015]. 
This finding is particularly notable given that, in previous cross-sectional data, this effect seems to be most strongly driven by infants younger than 4 months of age [e.g., @Fausey2016; @Jayaraman2015; @Sugden2014] who see both more frequent and more persistent faces [@Jayaraman2018]. 
We also found this to be true when restricting our analyses to full-field faces, suggesting this effect is not driven by a concurrent shift from more full-view to partial-views of faces.

Second, we also found an unexpectedly high proportion of hands in infants' view, even when restricting the field-of-view to the center field-of-view to make the viewpoints comparable to those of headcams used in prior work. 
Why might this be the case? One idea is that these videos contain the viewpoints of children not only during structured interactions (e.g., play sessions at home or in the lab) but during everyday activities when children may be playing by themselves or simply observing the actions of caregivers and other people in their environment. 
During these less structured times, caregivers may move about in the vicinity of the child but not interact with them as directly -- leading to views where a person and their hands are visible from a distance, but this person's face may be turned away from the infant or occluded (see examples in Figure 1). Indeed, using the same pose detector on videos from in-lab play sessions, @long2021automated found the opposite trend: slightly fewer hand detections than face detections from 8-16 months of age. Work that directly examines the variability in the social information in view across more vs. less structured activity contexts could further test this idea.

An analysis based on the location the videos were filmed in further highlights the variability of the social information in view during different activities, showing differences across locations and between individual children. Within a given, well-defined context -- e.g., mealtime in kitchens -- S saw more faces than A, and S saw more faces in the kitchen than in other locations. This variability likely stems from the fact that there are at least three ways to feed a young child: 1) sitting in front of the child, facing them as they sit in a high chair; 2) sitting behind the child, holding them as they face outward, and 3) sitting side by side. Each of these positions offer the child differing degrees of visual access to faces and hands. While the social information in view may be variable across children in different activity contexts, these analyses suggest they could be stable within a given child's day-to-day experience.

@@

Importantly, however, these automated detections do not entirely obviate the need for careful inspection and manual annotation of dense video data. While the present results suggest that OpenPose achieves moderate performance at detecting faces and hands in egocentric videos -- as does @Long2021automated -- these results do not guarantee that OpenPose will generalize with similar accuracy to other video datasets. By using manual annotations to estimate the accuracy of these automated techniques for their video datasets, researchers can weigh the pros and cons of automated detections for answering their particular research questions. While OpenPose does provide a considerable amount of about all of the people in a given image -- estimating the entire poses for every individual -- it may not always perform similarly in challenging viewpoints.

So, how might OpenPose -- or other pose detection algorithms -- be improved upon and used in future work? One promising direction may be to use detailed pose annotations of the people in the infant view to fine-tune later layers of pose detection networks. This has the potential to improve upon the overall accuracy of the network to detect the social information in infant egocentric videos and yield more reliable, detailed detections.  A second potential area for innovation lies in leveraging the dense nature of these large-scale annotations to improve model accuracy: By pooling detections from surrounding frames, we may be able to build classifiers that perform more accurately on a single challenging viewpoint. Finally, a third area for improvement consists of building classifiers that can accurately distinguish between children's hands (as seen from the egocentric point of view) versus adults' hands--a notoriously challenging problem in computer vision [@bambach2017lending]. We expect that these goals may become more and more feasible as we simultaneously improve the head-mounted cameras that are used in both at-home and in-lab studies; increasing the resolution and quality of the images we record will no doubt improve the ability of computer vision algorithms to extract detailed information from them.

More broadly, we believe that the adaptation of deep neural networks for the infant egocentric view remains a promising avenue for collaboration between computer vision experts and developmental psychologists. 
Indeed, this combination has already yielded new insights about the learning mechanisms needed to build visual representations [@tsutsui2020computational; @zhuang2020unsupervised; @orhan2020self]. 
We propose that the use of novel algorithms with large-scale analysis of dense datasets -- collected with different fields of view, cameras, and from many different laboratories -- will lead to generalizable conclusions about the regularities of infant experience that scaffold learning.
